### 2020-02-21 manuscript/ERL_global_C_review.Rmd
transferred more content

\newpage
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/C_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Table 1. ForC variables included in this analysis. Shown are variable names and descriptions, the associated variable name(s) in the database, and number of plots with records. Complete list of variables with full definitions is available at [GitHub url].", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12)  %>%
  pack_rows("Annual fluxes", 1, 21, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Stocks", 22, 32, latex_gap_space = "1em", colnum = 1, hline_before = FALSE)
```

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/C_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Table 1. ForC variables included in this analysis. Shown are variable names and descriptions, the associated variable name(s) in the database, and number of plots with records. Complete list of variables with full definitions is available at [GitHub url].", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12)  %>%
  pack_rows("Annual fluxes", 1, 21, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Stocks", 22, 32, latex_gap_space = "1em", colnum = 1, hline_before = FALSE)
```

Analyses drew from ForC-simplified (https://github.com/forc-db/ForC/blob/master/ForC_simplified), which is a rearrangement of ForC intended to facilitate analyses. In generating ForC-simplified, all measurements originally expressed in units of dry organic matter ($OM$) were converted to units of C using the IPCC default of $C = 0.47 * OM$ (IPCC 2006). Duplicate or otherwise conflicting records (indicated in conflicts field of MEASUREMENTS table) were reconciled as follows. Replicate measurements (i.e., replicates from within a single study) were averaged. Records that subsumed others— *i.e.*, the time period included that of $\ge$ 2 other records or dates were unknown and therefore conflicted with $\ge$ 2 other records—were removed. For each group of duplicate records—i.e., measurements of the same variable in the same plot at the same time—one record was assigned precedence (recorded in D.precedence field). When measurement periods overlapped or were not specified, precedence was given first to records representing longer measurement periods (*i.e.*, end.date - start.date) and then to more recently published values. We manually reviewed duplicates that differed only in methodology, assigning precedence to the record employing a more comprehensive approach (e.g., inclusion of understory, lianas, or bamboo as opposed to just trees) or using a favored methodology.

Records were filtered to remove plots that had undergone significant anthropogenic management or major disturbance since the most recent stand establishment (*i.e.*, that reflected by stand.age). Specifically, we removed all plots flagged as managed in ForC-simplified (managed field). This included plots with any record of managements manipulating CO2, temperature, hydrology, nutrients, or biota, as well as any plots whose site or plot name contained the terms “plantation”, "planted", “managed”, “irrigated”, or “fertilized”.  Plots flagged as disturbed in ForC-simplified included stands that had undergone anthropogenic thinning or partial harvest (“Cut” or “Harvest” codes) unless this was very minor (percent.mortality= “minor”). We retained sites that were grazed or had undergone low severity natural disturbances (<10% mortality) including droughts, major storms, fires, and floods. We also removed all plots for which no stand history information had been retrieved.

Data were analyzed to produce basic summaries of C cycle patterns across biomes and stand ages following an approach similar to that of Anderson-Teixeira et al (2016). For mature forests, to obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot, weighting flux measurements according to the length of measurement periods (i.e., end.date - start.date). Values were then averaged across plots clustered within 25 km of one another (geographic.area field of SITES table, sensu Anderson-Teixeira et al 2018), weighting by area.sampled (MEASUREMENTS table) or plot.area (PLOTS table) if available for all records. This step was taken to avoid pseudo-replication and to combine any records from sites with more than one name in ForC. Finally, we computed statistics with geographic.area as the unit of replication. To compare across biomes, [**Valentine, please describe**]. There were enough data to run this analysis for all focal variables but XX.

For young (<100yrs) forest types, we employed a mixed effects model (XX in R) with biome and log10[stand.age] as fixed effects and plot nested within geographic.area as a random effect. When the effect of stand.age was significant at p $\le$ 0.05 and when each biome had records for stands of at least 10 different ages, a biome - stand.age interaction was included in the model. In the C cycle schematics for young forests, we report equations based on these models. In cases where there was no significant effect of stand.age, records were averaged as for mature stands.

All database manipulation, analyses, and figure production were fully automated in R (version, citation). Materials required to fully reproduce these analyses, including data, R scripts, and image files, are archived in Zenodo (DOI: TBD]. Data, scripts, and results presented here are also available through the open-access ForC GitHub repository (https://github.com/forc-db/ForC), where many will be updated as the database develops.

### Review Results/ Synthesis
*(The Review Results/Synthesis section presents the findings of the analyses.)*

*C stocks and fluxes of mature forests*
	Average C cycles for tropical broadleaf, temperate broadleaf, temperate conifer, and boreal forests $\ge$ 100 years old and with no known major disturbance or significant anthropogenic management are presented in Figures 2-5, and statistics for each biome type are also summarized at: [GitHub URL]. Of the # flux and # stock variables mapped in these diagrams, ForC contained estimates from $\ge$ 7 distinct geographic areas for *#* fluxes and *#* stocks in tropical broadleaf forests, # fluxes and # stocks in temperate broadleaf forests, #fluxes and # stocks in temperate conifer forests, and fluxes and # stocks in boreal forests. For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets were generally consistent. That is, component fluxes and stocks summed to within 1 std of more inclusive fluxes in all but one instance (in temperate conifer forests, $aboveground woody biomass + foliage biomass > aboveground biomass + 1std$; Fig. 4). **This is based on my quick scan of the figures. Need to add a formal automated test: https://github.com/forc-db/ERL-review/issues/16 **
